The Etiology of Cybersecurity

### 2021-03-01 reports/paper_0/main.tex
manual merge with oliviero's branch

\newcommand{\fixn}[2]{{\bf FIX}\footnote{#1: #2}}

@@

\begin{abstract}
	The objective of this research is to lay the foundations for the
	development of a scientific theory that determines (all and only) the possible
	insecure and secure configurations of any abstract system. We claim
	that cybersecurity weaknesses (i.e. errors) are at the beginning of the
	causality chain that leads to cybersecurity attacks.  We, then,
	formulate a scientific (falsifiable by experiments) hypothesis that we
	use to predict all the weaknesses in the architectural design of an
	abstract system. The mathematical formulation of our hypothesis is
	based on a correlation between the epistemological concepts of
	knowledge, beliefs, and information with the engineering concepts of
	requirements, functional architectures, and channels.  Ultimately, our
	hypothesis allows for the definition of the cybersecurity of a system as a
	mathematical formula.  We implemented a prototype cybersecurity risk
	assessment tool that, based on our hypothesis, predicts the weaknesses in a
	UML model of a (cyber-physical) system.
\end{abstract}

@@

\section{Introduction}\label{sec:intro}
\paragraph{Context and motivation} 
A \emph{scientific theory} is an explanation of a phenomenon such that the
explanation follows the scientific method. The \emph{scientific method} is an
\emph{empirical} method that aims at mitigating potential fallacies in
theories.  Karl Popper famously argued (e.g. in \autocite{Popper1959logic})
that a scientific theory can never be verified but only falsified, that a
theory should not be conceived by using the principle of
induction\footnote{Albert  Einstein wrote to Popper: ``[...] and I think (like
you, by the way) that theory cannot be fabricated out of the results of
observation, but that it can only be invented.'' \autocite{Popper1959logic}},
and that empirical experiments should be considered as the only evidence to
support the non-falseness of a scientific theory. 
If we consider a natural (real-world) phenomenon, such as gravity, we can think
of a scientific theory as an \emph{abstract} mathematical formula (or a set of
formulas) that defines axiomatically a certain (natural) phenomenon in a
specific algebraic structure. While such a theory can be proved to be correct
within the mathematical setting it has been conceived in (e.g. with respect to
other axioms of the algebraic structure where it has been postulated, or with
respect to other background theories), no proof can be carried out to verify
that the theory properly abstracts the phenomenon it describes (i.e. that the
theory is a sound or complete approximation of the real phenomenon).
Similarly, the results of the application of a scientific theory (i.e. its
predictions) can be verified in the abstract mathematical structure but how can
we be sure that the theory correctly characterizes the phenomenon it describes? 
Popper's famous ``demarcation principle'' draws a line between scientific and
pseudo-scientific theories by proposing that a scientific theory can
be considered acceptable as long as no empirical experiment falsify it. For
example, a theory of gravity, in its mathematical setting, can predict how
objects attract each other, and those predictions can be tested by empirical
experiment. If the theory correctly represents the phenomenon, no empirical
experiment should falsify the predictions of that theory.

In \autocite{Herley2016unfalsifiability}, Cormac Herley explores what he calls
``an asymmetry in computer security'', which he defines as follows: ``Things
can be declared insecure by observation, but not the reverse. There is no
observation that allows us to declare an arbitrary system or technique
secure''. With security, Herley only focuses on cybersecurity (we also use
security and insecurity, in this paper, only to refer to cyber-insecurity and
cybersecurity) and his intuition is that there is no scientific theory that can
predict the cybersecurity of a system, nor a theory that can predict all
possible insecurities of a system (which, by negation may be used as a theory
of cybersecurity).  Herley then uses this argument to show that ``claims that
any measure is necessary for security are empirically unfalsifiable''. An
example is whether or not password masking makes a system secure. Password
masking prevents a complete leakage of the password, and a system, in which
password masking is implemented, is believed to be secure because an attacker
won't be seeing the password by ``shoulder surfing''.  This reasoning
is circular and it is always true that a system in which password masking is
implemented is a system in which a password is masked. No experiment can ever
falsify this statement.  Given that any theory that is not falsifiable by an
empirical experiment is well known\footnote{``A theory which is not refutable
by any conceivable event is nonscientific. Irrefutability is not a virtue of a
theory (as people often think) but a vice.'' -- Karl Popper, Conjectures and
Refutations \autocite{popper1962conjectures}.} to be nonscientific (i.e.
unfalsifiability is a fallacy of a theory), Herley concludes that there is no
scientific theory supporting this type of cybersecurity measures; generalizing,
cybersecurity seems to lay in the realm of pseudo-sciences
\autocite{Herley2016usenixvideo}. Herley, e.g.  in
\autocite{Herley2017justifying}, discusses the implications of a nonscientific
approach to cybersecurity, and highlights the tremendous impact on the
scientific research and engineering of systems. While the criticism is
investigated in \autocite{Herley2016unfalsifiability}, no solution is provided
nor envisioned.

@@

With our approach, a list of weaknesses emerges from the mathematical
formulation of a system in a framework called $\abftheory$-framework and
predicts 4 main classes of weaknesses. Those classes of weaknesses are used to
calculate all the insecurity configurations of all the components of a system,
obtaining a precise estimation of all potential cybersecurity-related risks in
any given system. Our hypothesis can be falsified by means of experiments,
testing if all the predicted weaknesses are present in the system under test,
or testing if other (not predicted by our hypothesis) weaknesses are present.
In fact, if any cybersecurity weaknesses were to be found in a system and not
predicted by our hypothesis, the hypothesis could be declared incomplete.  If a
cybersecurity weakness would be predicted by our hypothesis but found to be impossible
to realize, our hypothesis could be declared as wrong.

@@

In most of the natural languages the concepts of safety
and security are not syntactically differentiated and both terms (safety and
security) are expressed by the same word, e.g. sicurezza in Italian.  A
semantic distinction between safety and (cyber)security is correlated to a
belief\footnote{A belief has to be intended as a proposition which is supposed
to be true by the majority of people in our society, without a scientific
underlying theory but based on partial empirical evidences or inductive reasoning based on partial empirical evidences.} that
safety deals with \emph{accidents} (i.e. an unfortunate incident) posed by the
natural environment (e.g. natural events such as wearing of hardware
components), whereas cybersecurity deals with \emph{incidents} posed by mankind (e.g.
attackers and bugs). The fundamental difference between nature and mankind (and,
in turn, between safety and cybersecurity) is believed to be on the different
intents (incidents are intentional, whereas accidents are not) of the causes
that generates a threat. Namely, nature is believed not to have malicious
intents (but unfortunate causes-effects), whereas threats generated by mankind are
malicious\footnote{Of course, logical flaws or bugs may be
introduced by other means (e.g. ignorance) without explicit malicious intents,
but the exploitation of those flaws is considered (for now, and detailed
afterwards in the article) malicious, and thus we consider any vulnerability to
be malicious even if it is due to the lack of skills.}.
This conclusion seems to be against a general formulation of a cybersecurity theory;
how can we define a theory that predicts what a human being will do?
Cybersecurity attacks seem to be related to the creativity of the attacker
and thus unpredictable.

@@

\section{A Cybersecurity Hypothesis in the $\abftheory$-framework}\label{sec:hypothesis}
In order to address the problem raised by Herley, we shall define how to
distinguish between a secure and an insecure system. While most of the
literature have correlated the problem of in-security
to the maliciousness of agents interacting with the system, we show that
cybersecurity doesn't seem to stem from a malicious nature but, rather, insecurity
raises from the lack of well-defined cybersecurity requirements for the development
process of a system. We argue that the high number of cybersecurity vulnerability
reported today are simply the realization of potential system configurations,
which deviate from the nominal behavior because the \emph{intended (or
nominal) behavior} of the system is not precisely defined in the specification
at the very early stages of the engineering process.
As a reference, we consider the following steps of the engineering process
and our objective is to be able to predict the cybersecurity requirements
instead of axiomatically assume them.
\begin{enumerate}
	\item \emph{System Specification}, where the \emph{functional and physical requirements} are defined.
	\item \emph{Architecture Design}, where the specification is structured into \emph{functional and physical architectures}.
	\item \emph{Cybersecurity Risk Assessment}, where the potential \emph{weaknesses} (errors)
		are identified and, consequently, \emph{cybersecurity requirements} are
		captured.
	%\item \emph{Design Refinement}, where the physical and functional
	%	architectures are extended with \emph{mitigations} for the
	%	weaknesses. Mitigations at this step details the semantics of
	%	the functional blocks (behaviors), the data flow, and communication logic.
	%\item \emph{Verification of Security Requirements}, where the data flow, behaviors, and communication protocols are verified against the cybersecurity requirements.
\end{enumerate}
Given that, in our investigation, we changed the focus from the attacker to the
potential designs of a system, we start by defining a general framework for the definition
of a system. On top of this framework we will identify system weaknesses as potential
design errors.

@@

		difference between knowledge and belief (as epistemological
		concepts), and the whole Doxastic logic defines in details how

@@

		of information and the difference with knowledge and belief.

@@

		tuple of assertions, beliefs, and facts.

@@

knowledge, beliefs, and the information or assertions it provides; where
knowledge is defined, as in \autocite{Steup2020epistemology}, as a set of
propositions known by an agent, such that: (i) knowledge requires belief, (ii)
knowledge requires truth, (iii) knowledge must be \emph{properly justified}, and
the only objective of information is to exchange beliefs between agents.  As
defined in \autocite{Hintikka1993Information}, ``information is specified by
specifying which alternatives concerning the reality it admits and which
alternatives excludes''. This means that if we consider a propositional
variable (which admits the two alternatives True/False) its information is
defined as believed to be True/False and not believed to be the opposite.  Due
to the definition of information and then with its relation to the
probabilistic correlation to truth/reality, we consider information in relation
to an agent's beliefs. Similarly, we consider beliefs to define the actual
behavior of an agent or a system; i.e. we consider behaviors as belief revision
systems.
The difference between knowledge and information as used by Hintikka, and facts
and assertions as used in \autocite{Santaca2016abf}, are not precisely discussed
in \autocite{Santaca2016abf}.  Furthermore, those epistemological concepts are
difficult to define
\autocite{Gettier2012knowledge}.

@@

Instead, we now define those concepts abstractly, inspired by the

@@

Section~\ref{sec:theory} we detail them as engineering concepts.

@@

We give a graphical representation of (sub-)system and agent in Figure~\ref{fig:system-agent}.
The notation will be introduced in the next section but, intuitively,
Figure~\ref{fig:system-agent} shows a system composed by two agents. The system
has two ports denoted by ``I'' (with incoming assertions) and ``O'' (with outgoing assertions).
The bottom part of Figure~\ref{fig:system-agent} details the structure of a single
agent which is not decomposed into other (sub-)agents. In this case, ports translates
incoming assertions into beliefs that feeds the behavior block, and outgoing beliefs
from the behavior block are then translated back into (outgoing) assertions.

@@

\subsection{Mereo-topological Reasoning}
\begin{table*}[t]
\centering
\begin{tabular}{ccclll} 
\rota{\textbf{RCC3}}&\rota{\textbf{RCC5}}&\rota{\textbf{RCC8}}&\textbf{Terminology} & \textbf{Notation} & \textbf{Definition} \\
\hline
&&&Connects with 			& $\mathit{C}(\mathit{X},\mathit{Y})$ 		& $\mathit{X}\subseteq \mathit{Y}$ \\
&&&Disconnected from		& $\neg \mathit{C}(\mathit{X},\mathit{Y})$		& $\mathit{X}\not\subseteq \mathit{Y}$\\
&&&Part of				& $\mathit{P}(\mathit{X},\mathit{Y})$		& $\forall \mathit{Z} ~\mathit{C}(\mathit{Z},\mathit{X}) \rightarrow \mathit{C}(\mathit{Z},\mathit{Y})$\\
&&&Overlaps			& $\mathit{O}(\mathit{X},\mathit{Y})$		& $\exists \mathit{Z} ~\mathit{P}(\mathit{Z},\mathit{X})\wedge \mathit{P}(\mathit{Z},\mathit{Y})$\\
\Tdot&&&  \textbf{Overlaps Not Equal} 	& $\mathit{ONE}(\mathit{X},\mathit{Y})$		& $\mathit{O}(\mathit{X},\mathit{Y}) \land \neg \mathit{EQ}(\mathit{X},\mathit{Y})$ \\
\Tdot&\Tdot&\Tdot& \textbf{Equal to} 		& $\mathit{EQ}(\mathit{X},\mathit{Y})$  		& $\mathit{P}(\mathit{X},\mathit{Y}) \wedge \mathit{P}(\mathit{Y},\mathit{X})$\\
\Tdot&\Tdot&\Tdot& \textbf{DiscRete from} 		& $\mathit{DR}(\mathit{X},\mathit{Y})$		& $\neg \mathit{O}(\mathit{X},\mathit{Y})$\\
&\Tdot&\Tdot&\textbf{Partial-Overlap}	& $\mathit{PO}(\mathit{X},\mathit{Y})$ 		& $\mathit{O}(\mathit{X},\mathit{Y})\wedge \neg \mathit{P}(\mathit{X},\mathit{Y}) \wedge \neg \mathit{P}(\mathit{Y},\mathit{X})$\\ 
&\Tdot&&\textbf{Proper-Part-of} 	& $\mathit{PP}(\mathit{X},\mathit{Y})$ 		& $\mathit{P}(\mathit{X},\mathit{Y})\wedge \neg \mathit{P}(\mathit{Y},\mathit{X})$\\ 
	&\Tdot&&\textbf{Proper-Part-of-\textit{\textbf{i}}nverse} & $\mathit{PPi}(\mathit{X},\mathit{Y})$ 		& $\mathit{P}(\mathit{Y},\mathit{X}) \wedge \neg \mathit{P}(\mathit{X},\mathit{Y})$\\
&&\Tdot&\textbf{Externally Connected} 	& $\mathit{EC}(\mathit{X},\mathit{Y})$ 		& $\mathit{C}(\mathit{X},\mathit{Y}) \wedge \neg\mathit{O}(\mathit{X},\mathit{Y})$\\ 
&&\Tdot&\textbf{Tangential PP} 	& $\mathit{TPP}(\mathit{X},\mathit{Y})$ 		& $\mathit{PP}(\mathit{X},\mathit{Y})\wedge\exists\mathit{Z}~[\mathit{EC}(\mathit{Z},\mathit{X}),\mathit{EC}(\mathit{Z},\mathit{Y})]$\\ 
&&\Tdot&\textbf{Tangential PPi} 	& $\mathit{TPPi}(\mathit{X},\mathit{Y})$ 		& $\mathit{TPP}(\mathit{Y},\mathit{X})$\\ 
&&\Tdot&\textbf{Non-Tangential PP} 	& $\mathit{NTPP}(\mathit{X},\mathit{Y})$ 		& $\mathit{PP}(\mathit{X},\mathit{Y})\wedge\neg\exists\mathit{Z}~[\mathit{EC}(\mathit{Z},\mathit{X}),\mathit{EC}(\mathit{Z},\mathit{Y})]$\\ 
&&\Tdot&\textbf{Non-Tangential PPi} 	& $\mathit{NTPPi}(\mathit{X},\mathit{Y})$ 		& $\mathit{NTPP}(\mathit{Y},\mathit{X})$\\ 
\end{tabular}
\caption{RCC3, RCC5, and RCC8 relations between regions $X$, $Y$ and $Z$ ~\label{tab:rcc358}~\label{tab:rcc}}
\end{table*}

>>>>

@@

\begin{abstract}
	The objective of this research is to lay the foundations for the
	development of a scientific theory that determines (all and only) the
	possible insecure and secure configurations of any abstract system. We
	claim that cybersecurity weaknesses (i.e. errors) are at the beginning
	of the causality chain that leads to cybersecurity attacks.  We, then,
	formulate a scientific (falsifiable by experiments) hypothesis that we
	use to predict all the weaknesses in the architectural design of an
	abstract system. The mathematical formulation of our hypothesis is
	based on a correlation between the epistemological concepts of
	facts, beliefs, and assertions with the engineering concepts of
	requirements, functional architectures, and channels.  Ultimately, our
	hypothesis allows for the definition of a mathematical formula which
	describes the cybersecurity of a system.  We implemented a prototype
	cybersecurity risk assessment tool that, based on our hypothesis,
	predicts the weaknesses in a UML model of a (cyber-physical) system.
\end{abstract}

@@

\fixnote{Oliviero}{Two general remarks. First, I'd maybe specify more what concretely A, B and F "look like", if that makes sense. How do we concretely specify a fact in the ABF framework? If I am not mistaken, RCC defines axiomatically how in general a mereotopology should be, and a *concrete* mereotopology corresponds to a particular system specification. Is this correct? If so, make explicit how one would encode this, if this make sense. At the very end you talk about a particular configuration being SAT w.r.t. the algebraic strucutre; is this algebraic structure, indeed, the system specification? You also sometimes speak about logic formulas; what is the connection between these logical formulas and regions? Is a region a "set" of logical formulas, or is it that a region is logically defined?

Secondly, and this is probably due to my inexperience with systems design (and ABF), it is not totally clear to me exactly what a belief is; more concretely, what is the difference between assertions and beliefs. Beliefs define the inputs and the outputs; assertions are what is exchanged between agents. Wouldn't the assertions already define the inputs and outputs? or are the beliefs the "expected" I/Os, while assertions are the "actual" I/Os? Indeed, a functional block is defined by its inputs/outputs. Then, if EQ(F,A) hold, aren't we already happy? Because, if all the inputs and outputs are compliant with your requirements, your system is functionally "correct", and behaves as you want. Am I mistaken? Perhaps there are some other aspects that I am not considering.}

\fixnote{Oliviero}{Question: the region F encodes the requirements. Then, what if we encode a requirement wrongly? or, what if we do not realise that some implict requirements are missing? Indeed, one might not see why integrity is a requirement until a breach happens. Is this within the scope of the theory? Finally; are we sure that all reasonable requirements can be encoded in the region F?}

\section{Introduction}\label{sec:intro}
\paragraph{Context and motivation} 
A \emph{scientific theory} is an explanation of a phenomenon such that the
explanation follows the scientific method. The \emph{scientific method} is an
\emph{empirical} method that aims at mitigating potential fallacies in
theories.  Karl Popper famously argued (e.g. in \autocite{Popper1959logic})
that a scientific theory can never be verified but only falsified, that a
theory should not be conceived by using the principle of
induction\footnote{Albert  Einstein wrote to Popper: ``[...] and I think (like
you, by the way) that theory cannot be fabricated out of the results of
observation, but that it can only be invented.'' \autocite{Popper1959logic}},
and that empirical experiments should be considered as the only evidence to
support the non-falseness of a scientific theory. 
If we consider a natural (real-world) phenomenon, such as gravity, we can think
of a scientific theory as an \emph{abstract} mathematical formula (or a set of
formulas) that defines axiomatically a certain (natural) phenomenon in a
specific algebraic structure. While such a theory can be proved to be correct
within the mathematical setting it has been conceived in (e.g. with respect to
other axioms of the algebraic structure where it has been postulated, or with
respect to other background theories), no proof can be carried out to verify
that the theory properly abstracts the phenomenon it describes (i.e. that the
theory is a sound or complete approximation of the real phenomenon).
Similarly, the results of the application of a scientific theory (i.e. its
predictions) can be verified in the abstract mathematical structure, but how can
we be sure that the theory correctly characterizes the phenomenon it describes? 
Popper's famous ``demarcation principle'' draws a line between scientific and
pseudo-scientific theories by proposing that a scientific theory can
be considered acceptable as long as no empirical experiment falsify it. For
example, a theory of gravity, in its mathematical setting, can predict how
objects attract each other, and those predictions can be tested by empirical
experiment. If the theory correctly represents the phenomenon, no empirical
experiment should falsify the predictions of that theory.

In \autocite{Herley2016unfalsifiability}, Cormac Herley explores what he calls
``an asymmetry in computer security'', which he defines as follows: ``Things
can be declared insecure by observation, but not the reverse. There is no
observation that allows us to declare an arbitrary system or technique
secure''. With security, Herley only focuses on cybersecurity (we also use
security and insecurity, in this paper, only to refer to cyber-insecurity and
cybersecurity) and his intuition is that there is no scientific theory that can
predict the cybersecurity of a system, nor a theory that can predict all
possible insecurities of a system (which, by negation, may be used as a theory
of cybersecurity).  Herley then uses this argument to show that ``claims that
any measure is necessary for security are empirically unfalsifiable''. An
example is whether or not password masking makes a system secure. Password
masking prevents a complete leakage of the password, and a system, in which
password masking is implemented, is believed to be secure because an attacker
won't be seeing the password by ``shoulder surfing''.  This reasoning
is circular and it is always true that a system in which password masking is
implemented is a system in which a password is masked. No experiment can ever
falsify this statement\footnote{In other words, one cannot design an experiment to show that
password masking is not secure or unnecessary, and a correlated problem is that
this may lead to a scenario where more measures are added but there is no good
way of saying which measures are superflous.}. Given that any theory that is not falsifiable by an
empirical experiment is well known\footnote{``A theory which is not refutable
by any conceivable event is nonscientific. Irrefutability is not a virtue of a
theory (as people often think) but a vice.'' -- Karl Popper, Conjectures and
Refutations \autocite{popper1962conjectures}.} to be nonscientific (i.e.
unfalsifiability is a fallacy of a theory), Herley concludes that there is no
scientific theory supporting this type of cybersecurity measures; generalizing,
cybersecurity seems to lay in the realm of pseudo-sciences
\autocite{Herley2016usenixvideo}. Herley, e.g.  in
\autocite{Herley2017justifying}, discusses the implications of a nonscientific
approach to cybersecurity, and highlights the tremendous impact on the
scientific research and engineering of systems. While the criticism is
investigated in \autocite{Herley2016unfalsifiability}, no solution is provided
nor envisioned.

@@

With our approach, a list of weaknesses emerges from the mathematical
formulation of a system in a framework called $\abftheory$-framework, and
predicts 4 main classes of weaknesses. Those classes of weaknesses are used to
calculate all the insecurity configurations of all the components of a system,
obtaining a precise estimation of all potential cybersecurity-related risks in
any given system. Our hypothesis can be falsified by means of experiments,
testing if all the predicted weaknesses are present in the system under test,
or testing if other (not predicted by our hypothesis) weaknesses are present.
In fact, if any cybersecurity weaknesses were to be found in a system and not
predicted by our hypothesis, the hypothesis could be declared incomplete.  If a
cybersecurity weakness would be predicted by our hypothesis but found to be impossible
to realize, our hypothesis could be declared as wrong.

@@

In most of the natural languages the concepts of safety
and security are not syntactically differentiated and both terms (safety and
security) are expressed by the same word, e.g. ``sicurezza'' in Italian.  A
semantic distinction between safety and (cyber)security is correlated to a
belief\footnote{A belief has to be intended as a proposition which is supposed
to be true but no conclusive evidence makes it known to be true.} that
safety deals with \emph{accidents} (i.e. an unfortunate incident) posed by the
natural environment (e.g. natural events such as wearing of hardware
components), whereas cybersecurity deals with \emph{incidents} posed by mankind (e.g.
attackers and bugs). The fundamental difference between nature and mankind (and,
in turn, between safety and cybersecurity) is believed to be on the different
intents (incidents are intentional, whereas accidents are not) of the causes
that generates a threat. Namely, nature is believed not to have malicious
intents (but unfortunate causes-effects), whereas threats generated by mankind are
malicious\footnote{Of course, logical flaws or bugs may be
introduced by other means (e.g. ignorance) without explicit malicious intents,
but the exploitation of those flaws is considered (for now, and detailed
afterwards in the article) malicious, and thus we consider any vulnerability to
be malicious even if it is due to the lack of skills.}.
This conclusion seems to be against a general formulation of a cybersecurity theory;
how can we define a theory that predicts what a human being will do?
Cybersecurity attacks seem to be related to the creativity of the attacker
and thus unpredictable.

@@

\section{A Cybersecurity Hypothesis in the $\abftheory$-framework}\label{sec:hypothesis}
In order to address the problem raised by Herley, we shall define how to
distinguish between a secure and an insecure system. While most of the
literature have correlated the problem of in-security
to the maliciousness of agents interacting with the system, we show that
cybersecurity doesn't seem to stem from a malicious nature but, rather, insecurity
raises from the lack of well-defined cybersecurity requirements for the development
process of a system. We argue that the high number of cybersecurity vulnerability
reported today are simply the realization of potential system configurations,
which deviate from the  \emph{intended (or
nominal) behavior} because the nominal behavior of the system is not precisely defined in the specification
at the very early stages of the engineering process.
As a reference, we consider the following steps of the engineering process
and our objective is to be able to predict the cybersecurity requirements
instead of axiomatically assume them.
\begin{enumerate}
	\item \emph{System Specification}, where the \emph{functional and physical requirements} are defined.
	\item \emph{Architecture Design}, where the specification is structured into \emph{functional and physical architectures}.
	\item \emph{Cybersecurity Risk Assessment}, where the potential \emph{weaknesses} (errors)
		are identified and, consequently, \emph{cybersecurity requirements} are
		captured.
	%\item \emph{Design Refinement}, where the physical and functional
	%	architectures are extended with \emph{mitigations} for the
	%	weaknesses. Mitigations at this step details the semantics of
	%	the functional blocks (behaviors), the data flow, and communication logic.
	%\item \emph{Verification of Security Requirements}, where the data flow, behaviors, and communication protocols are verified against the cybersecurity requirements.
\end{enumerate}
Given that, in our investigation, we changed the focus from the attacker to the
potential designs of a system, we start by defining a general framework for the definition
of a system. On top of this framework we will identify system weaknesses as potential
design errors.

@@

		belief (as epistemological
		concepts) and their relation with knowledge,
		and the whole Doxastic logic defines in details how

@@

		of information (and the difference with knowledge and belief).

@@

		tuple of assertions, beliefs, and facts. A detailed discussion
		on facts and assertions can be found in \autocite{facts2007stanford} and
		\autocite{assertion2007stanford} respectively.

@@

beliefs, and the information or assertions it provides.
%knowledge, beliefs, and the information or assertions it provides; where
%knowledge is defined, as in \autocite{Steup2020epistemology}, as a set of
%propositions known by an agent, such that: (i) knowledge requires belief, (ii)
%knowledge requires truth, (iii) knowledge must be \emph{properly justified}, and
%the only objective of information is to exchange beliefs between agents.
As in \autocite{Steup2020epistemology}, the only objective of information is to
exchange beliefs between agents and, as defined in \autocite{Hintikka1993Information},
``information is specified by specifying which alternatives concerning the
reality it admits and which alternatives excludes''. This means that if we
consider a propositional variable (which admits the two alternatives
True/False) its information is defined as believed to be True/False and not
believed to be the opposite.  Due to the definition of information and then
with its relation to the probabilistic correlation to truth/reality, we
consider information in relation to an agent's beliefs. Similarly, we consider
beliefs to define the actual behavior of an agent or a system; i.e. we consider
behaviors as belief revision systems.
%The difference between knowledge and information as used by Hintikka, and facts
The concepts of facts and assertions as used in \autocite{Santaca2016abf}, are
not precisely discussed in \autocite{Santaca2016abf}.  Furthermore, those
epistemological concepts are difficult to define
\autocite{Gettier2012knowledge} in general.

@@

Instead, we now define those concepts informally, inspired by the

@@

Section~\ref{sec:theory} we detail them, and properly define them, as engineering concepts.
\fixnote{Oliviero}{Is that actually what is happening? During this section III, we refer multiple times to engineering concepts such as system, functional specification and what not. We sometimes refer to the relationship between functional architecture and beliefs but that is not made precise. Maybe we should use only abstract terms, until the connection with those engineering aspects are introduced thoroughly? {\bf mr}: what I wanted to say here (and I probably failed) is that we define A, B, and F informally (and I changed abstractly with informally in the text) but we'll define them more precisely (and as engineering concept) later on. I modified the sentence to make this clearer but it seems to me to me that you're saying that the text is unnecessarily complicated by the mixed used of generic terms as beliefs and functional blocks/architecture. If that is the case we should definitely make the section clearer.}

@@

\fixnote{Oliviero}{There are some parts I am perplexed about about this section from "There is no agreement..." up to here). It is unclear to me why we present and define the general concept of knowledge rather then the concept of fact, since we use mostly "facts" and as defined in [41] an agent is cmposed by assertions, beliefs and facts (and not knowledge). Indeed, it seems from your last bullet point that a fact is a particular case of knowledge (as you say, "more general"), but the exact definition of fact is not really clear from here, at least to me. Further; why are facts requirements? Intuitively, I would define a fact to be something that is true; requirements are something that we *want* to be true. I understood why we do so later on in the paper; we are later on interested, by RCC, in whether the beliefs of our agents are consistent (EQ) with the facts, that is, we want our system to behave consistently with the requirements. I would maybe make this explicit: we interpret requirements as facts, since we consider them to be the truth, towards which our agents must be compliant with (rather than: facts are requirements and not the actual truth). Another thing I found to be unclear is your definition of belief. You start by saying that we will define these things abstractly but you refer here to a very system-oriented definition of belief: inputs and outputs. Indeed, you say that beliefs define the behaviour, but the exact definition of belief was not super clear to me. {\bf mr}: I think you're right and the key points are (i) what's a fact? (ii) why stressing knowledge if abf is based on facts? (iii) what's the relation between facts and requirements? A fact is a statement which is taken as true. it's not necessarily true in general but the discussion is much complex (unfortunately). I wanted to add it to the paper but someone said that it may be tricky since those concepts have been used for 2k years at least. But, as an example, ``Socrates is a man'' is a fact (i.e. a true statement or, better, a statement taken as true), right? do we \emph{know} it? how? did we induce it from empirical evidences by testing every single man ever existed? I guess you see what I mean. So, in my limited view, facts are statement taken as true, knowledge can be expressed by true statements, and requirements are statement taken as true (by developers and everyone else). The link between those concepts seems rather strong but I think you are suggesting to simplify the text changing the focus on facts or detailing the relation between knowledge and facts. I chose the former and changed the text accordingly.}

We give a graphical representation of (sub-)system and agent in Figure~\ref{fig:system-agent}.
The notation will be introduced in the next section but, intuitively,
Figure~\ref{fig:system-agent} shows a system composed by two agents. The system
has two ports denoted by ``I'' (with incoming assertions) and ``O'' (with outgoing assertions).
The bottom part of Figure~\ref{fig:system-agent} details the structure of a single
agent which is not decomposed into other (sub-)agents. In this case, ports translates
incoming assertions into beliefs that feeds the behavior block, and outgoing beliefs
from the behavior block are then translated back into (outgoing) assertions.

@@

\fixnote{Oliviero}{Further: what is a region? Is it a "prime" concept, that is, a primitive concept? Or is it a set? if it is a primitive concept, then defining connectedness in terms of set operations such as $\subseteq$ is a little counterintuitive; if a region is a set (or some other well-known mathematical concept), then state so explicitly somewhere, imho (as I said at the beginning, explicitly describing how these ABF regions look like would make this much clearer, I think). {\bf mr} you're right. it's a primitive concept, I changed it in the tab and in the text.}

\subsection{Mereo-topological Reasoning}
\begin{table*}[t]
\centering
\begin{tabular}{ccclll} 
\rota{\textbf{RCC3}}&\rota{\textbf{RCC5}}&\rota{\textbf{RCC8}}&\textbf{Terminology} & \textbf{Notation} & \textbf{Definition} \\
\hline
&&&Connects with 			& $\mathit{C}(\mathit{X},\mathit{Y})$ 		& reflexive and symmetric \\
&&&Disconnected from		& $\neg \mathit{C}(\mathit{X},\mathit{Y})$		& irreflexive or antisymmetric\\
&&&Part of				& $\mathit{P}(\mathit{X},\mathit{Y})$		& $\forall \mathit{Z} ~\mathit{C}(\mathit{Z},\mathit{X}) \rightarrow \mathit{C}(\mathit{Z},\mathit{Y})$\\
&&&Overlaps			& $\mathit{O}(\mathit{X},\mathit{Y})$		& $\exists \mathit{Z} ~\mathit{P}(\mathit{Z},\mathit{X})\wedge \mathit{P}(\mathit{Z},\mathit{Y})$\\
\Tdot&\Tdot&\Tdot& \textbf{Equal to} 		& $\mathit{EQ}(\mathit{X},\mathit{Y})$  		& $\mathit{P}(\mathit{X},\mathit{Y}) \wedge \mathit{P}(\mathit{Y},\mathit{X})$\\
\Tdot&&&  \textbf{Overlaps Not Equal} 	& $\mathit{ONE}(\mathit{X},\mathit{Y})$		& $\mathit{O}(\mathit{X},\mathit{Y}) \land \neg \mathit{EQ}(\mathit{X},\mathit{Y})$ \\
\Tdot&\Tdot&\Tdot& \textbf{DiscRete from} 		& $\mathit{DR}(\mathit{X},\mathit{Y})$		& $\neg \mathit{O}(\mathit{X},\mathit{Y})$\\
&\Tdot&\Tdot&\textbf{Partial-Overlap}	& $\mathit{PO}(\mathit{X},\mathit{Y})$ 		& $\mathit{O}(\mathit{X},\mathit{Y})\wedge \neg \mathit{P}(\mathit{X},\mathit{Y}) \wedge \neg \mathit{P}(\mathit{Y},\mathit{X})$\\ 
&\Tdot&&\textbf{Proper-Part-of} 	& $\mathit{PP}(\mathit{X},\mathit{Y})$ 		& $\mathit{P}(\mathit{X},\mathit{Y})\wedge \neg \mathit{P}(\mathit{Y},\mathit{X})$\\ 
	&\Tdot&&\textbf{Proper-Part-of-\textit{\textbf{i}}nverse} & $\mathit{PPi}(\mathit{X},\mathit{Y})$ 		& $\mathit{P}(\mathit{Y},\mathit{X}) \wedge \neg \mathit{P}(\mathit{X},\mathit{Y})$\\
&&\Tdot&\textbf{Externally Connected} 	& $\mathit{EC}(\mathit{X},\mathit{Y})$ 		& $\mathit{C}(\mathit{X},\mathit{Y}) \wedge \neg\mathit{O}(\mathit{X},\mathit{Y})$\\ 
&&\Tdot&\textbf{Tangential PP} 	& $\mathit{TPP}(\mathit{X},\mathit{Y})$ 		& $\mathit{PP}(\mathit{X},\mathit{Y})\wedge\exists\mathit{Z}~[\mathit{EC}(\mathit{Z},\mathit{X}),\mathit{EC}(\mathit{Z},\mathit{Y})]$\\ 
&&\Tdot&\textbf{Tangential PPi} 	& $\mathit{TPPi}(\mathit{X},\mathit{Y})$ 		& $\mathit{TPP}(\mathit{Y},\mathit{X})$\\ 
&&\Tdot&\textbf{Non-Tangential PP} 	& $\mathit{NTPP}(\mathit{X},\mathit{Y})$ 		& $\mathit{PP}(\mathit{X},\mathit{Y})\wedge\neg\exists\mathit{Z}~[\mathit{EC}(\mathit{Z},\mathit{X}),\mathit{EC}(\mathit{Z},\mathit{Y})]$\\ 
&&\Tdot&\textbf{Non-Tangential PPi} 	& $\mathit{NTPPi}(\mathit{X},\mathit{Y})$ 		& $\mathit{NTPP}(\mathit{Y},\mathit{X})$\\ 
\end{tabular}
\caption{RCC3, RCC5, and RCC8 relations between regions $X$, $Y$ and $Z$ ~\label{tab:rcc358}~\label{tab:rcc}}
\end{table*}
